---
title: "My First Report"
author: "Megan Kadzirange"
format:
  html:
    embed-resources: true
---

## Welcome to your practice report

This is a **Quarto** document. It mixes ordinary writing with live code, so your
report and your analysis always stay in sync. When you click **Render**, Quarto
runs the code below and builds a finished HTML page.

Try it now: change `author: "Your Name"` in the header above to your own name,
then click **Render**.

## A first look at the data

The code chunk below reads a small practice dataset from the `data/` folder and
shows the first few rows.

```{r}
patients <- read.csv("data/patients.csv")
head(patients)
```

## A first chart

```{r}
hist(patients$age,
     main = "Age distribution of practice patients",
     xlab = "Age (years)",
     col  = "steelblue")
```

## Your turn

## My Notes

I noticed that keeping your writing clear and concise helps reduce messiness when 
looking back at your work.
I also noticed the colour coding helps draw your attention to what is most important and to differentiate diffent parts of your code and writing.
Finally I learnt how to **bold** items in quarto 

## My R Code

```{r}
patients <- read.csv("data/patients.csv")
tail(patients)
```


When you are happy with the result, **commit and sync** your work (the Week 2
course page walks you through this), then submit your repository link on Canvas.
