---
title: "Assignment 2 Starter Analysis"
format: html
---

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)  # AI-EDIT(2026-06-23): tidyverse-default — consolidated core library() calls into library(tidyverse)
```

## Load Data

```{r}
nhanes <- read_csv("examples/nhanes-equity/data/nhanes_equity_v6.csv", show_col_types = FALSE)
```

## Inspect

```{r}
dim(nhanes)
names(nhanes)
glimpse(nhanes)
colSums(is.na(nhanes))
```

## Patients Aged 20 to 30

```{r}
patients_20_30 <- nhanes |>
  filter(Age >= 20, Age <= 30) |>
  select(Gender, Age, BMI) |>
  group_by(Gender)

patients_20_30
```

## Summarize

Replace this example with your own summary if you choose a different question.

```{r}
bmi_summary <- nhanes |>
  filter(!is.na(BMI), !is.na(IncomeGroup)) |>
  group_by(IncomeGroup) |>
  summarise(
    n = n(),
    mean_bmi = mean(BMI),
    .groups = "drop"
  )

bmi_summary
```

## Function

```{r}
mean_with_n <- function(x) {
  tibble(
    n = sum(!is.na(x)),
    mean = mean(x, na.rm = TRUE)
  )
}

mean_with_n(nhanes$BMI)

standard_deviation <- function(x) {
  sd(x, na.rm = TRUE)
}

standard_deviation(nhanes$BMI)
```

## Save Output

```{r}
dir.create("assignments/assignment02-r-with-ai/submission/output", recursive = TRUE, showWarnings = FALSE)
write_csv(bmi_summary, "assignments/assignment02-r-with-ai/submission/output/summary_table.csv")
```

## AI Audit Note

Add comments explaining which parts were drafted or debugged with AI and how you verified the result.

#HW Assignment 2
```{r}
library(readr)
library(dplyr)
```

I loaded the readr and dplyr libraries to read the CSV file and manipulate the data.

```{r}
nhanes <- read_csv("examples/nhanes-equity/data/nhanes_equity_v6.csv", show_col_types = FALSE)
```

Next I loaded the NHANES dataset from the specified CSV file.

```{r}
dim(nhanes)
names(nhanes)
glimpse(nhanes)
summary(nhanes)
colSums(is.na(nhanes))
```

Next I inspected my data to understand its structure, dimensions and missingness.

I then created a new data frame called patients_20_30 that filters the NHANES dataset for patients aged 20 to 30, selects the Gender, Age, and BMI columns, and groups the data by Gender.

I then created a custom standard deviation function.

#AI Audit Note: 
I used AI to help me write the code for loading the data, inspecting it, filtering it, and summarizing it. I verified the results by checking the output of each step and ensuring that the data was correctly filtered and summarized. I also cross checked it with the textbook notes. I also checked the output of the custom standard deviation function to ensure it was working correctly.